Enabling Ambient Backscatter \\Using a Low-Cost Software Defined Radio

### 2017-05-15 paper.tex
Alternative author block for improved formatting

\author{\IEEEauthorblockN{Maximilian Stiefel}
\IEEEauthorblockA{Uppsala University\\
maximilian.stiefel.8233@student.uu.se}
\and
\IEEEauthorblockN{Elmar van Rijnswou}
\IEEEauthorblockA{Uppsala University\\
elmar.vanrijnswou.9818@student.uu.se}
\and
\IEEEauthorblockN{Carlos Pérez-Penichet}
\IEEEauthorblockA{Uppsala University\\
carlos.penichet@it.uu.se                              }
\and
\IEEEauthorblockN{Ambuj Varshney}
\IEEEauthorblockA{Uppsala University\\
ambuj.varshney@it.uu.se}
\and
\IEEEauthorblockN{Christian Rohner}
\IEEEauthorblockA{Uppsala University\\
christian.rohner@it.uu.se}
\and
\IEEEauthorblockN{Thiemo Voigt}
\IEEEauthorblockA{Uppsala University\\
and RISE SICS\\
thiemo@sics.se}}

>>>>

\author{\IEEEauthorblockN{Maximilian Stiefel\IEEEauthorrefmark{1}, Elmar van Rijnswou\IEEEauthorrefmark{1}\\ 
Carlos Pérez-Penichet\IEEEauthorrefmark{1} Ambuj Varshney\IEEEauthorrefmark{1}, 
Christian Rohner\IEEEauthorrefmark{1} and Thiemo Voigt\IEEEauthorrefmark{2}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Uppsala University}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Uppsala Univerisyt and RISE SICS}}
